---
title: "miscellaneous"
author: "Steffen Ehrmann"
date: "11/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This scripts contains various operations to visualise stuff and check up on the data

```{r, load packages}
root <- "/home/se87kuhe/Nextcloud/geohack19"
```

```{r, load packages}
library(raster)
library(sf)
library(readr)
library(magritts)
library(tibble)
```

# Read in point data

We have extracted data on wells and pumps from the OSM database via the website www.oscar-web.de with the search querry `thailand (@pump + @man_made:water_well + @man_made:pump)`.
Those data are read in here for visualisation.

```{r}
water_sources <- read_sf(paste0(root, "/data/samples/SE_Asia.shp"))
```


# Extract names

We need a name for all the bore holes.

```{r}
# read in bore locations and their profiles and make a complete
bores_prof <- read_csv(file = paste0(root, "/data/waterpoints/gwBores-profile.csv"))
bores <- st_read(dsn = paste0(root, "/data/waterpoints/gwBores.geojson")) %>% 
  bind_cols(bores_prof) %>% 
  mutate(groundwaterProbability = round(probability, 1),
         temperatureMax = round(temperatureMax, 1),
         popDens = round(popDens, 1)) %>% 
  select(-x, -y, -probability)

boundaries <- list.files(paste0(root, "/data/admin"), pattern = "gpkg$")

# go through all countries and contstruct an object that contains only name and geometry
for(i in seq_along(boundaries)){
  
  layers <- st_layers(dsn = paste0(root, "/data/admin/", boundaries[i]))
  theLayer <- layers$name[which.max(layers$features)] # take names always from the "smallest" admin unit
  
  temp <- st_read(dsn = paste0(root, "/data/admin/", boundaries[i]),
                  layer = theLayer)
  
  theNames <- names(temp)
  outNames <- theNames[grep(x = theNames, pattern = "^NAME_")]
  outNames <- outNames[length(outNames)]
  
  temp <- temp %>% 
    select(name = outNames, geom)
  
  if(i == 1){
    out <- temp
  } else {
    out <- rbind(out, temp)
  }
}

# intersect bore locations with countries to extract names and replace
# duplicated names with names and numbers
bores <- st_intersection(x = bores, y = out) %>% 
  group_by(name) %>% 
  mutate(name2 = paste0(name, "_", 1:n())) %>% 
  ungroup() %>% 
  mutate(spotname = name2) %>% 
  select(-name2, -name)

st_write(obj = bores, dsn = paste0(root, "/data/waterpoints/gwBores_edit.geojson"))
```
